Target Markdown

### 2024-02-22 _targets.Rmd
Add SEM sensibility analysis

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
```

@@

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = tibble::tibble(
  names = c("no_rerun", "non_allo_no_rerun", "rerun")
    ),
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    }
  ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

@@

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("no_rerun", "non_allo_no_rerun", "rerun")
    )
```

@@

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

```{r targets group-all-analysis}
list(
  tar_target(sem_simplified_eff_tab_tot,
    tibble(
      sim_type = map_tibble$names,
      data = list(sem_simplified_eff_tab_no_rerun,
        sem_simplified_eff_tab_non_allo_no_rerun, sem_simplified_eff_tab_rerun)
      ) %>%
    unnest(cols = data)),
  tar_target(p_sem_simplified_eff_tab_tot,
    sem_simplified_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)

```{r, eval = FALSE}
tar_load(c(sem_simplified_collinearity_no_rerun, sem_simplified_collinearity_rerun,
    sem_simplified_collinearity_non_allo_no_rerun))
sem_simplified_collinearity_no_rerun %>%
  print(n = 30)
sem_simplified_collinearity_rerun %>%
  print(n = 30)
sem_simplified_collinearity_non_allo_no_rerun %>%
  print(n = 30)
```

@@

```{r, eval = FALSE}
tar_load(sem_simplified_eff_tab_tot)

@@

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```
```{r fig-sem-tot-sensibility}
ggsave_multiple(
  paste0("p_sem_simplified_eff_tab_tot", c(".jpg", ".png", ".pdf")),
  plot = tar_read(p_sem_simplified_eff_tab_tot),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm")
```
